Embedded Scalars, Preferred Readings \& Prosody: {A}n Experimental Revisit

### 2015-02-03 text/paper/revision_01/paper.tex
K2 1st revision initial export

\usepackage{../../helpers/gb4e_micha}
\usepackage{../../helpers/proofing}

\usepackage{../../helpers/mycommands}
% \usepackage{../helpers/myenvironments}

@@

\title{Embedded Scalars, Preferred Readings \& Intonation: {A}n
  Experimental Revisit} 
\author{% Fabian
  % Schlotterbeck, Michael Franke and Petra Augurzky
} 
\date{}

@@

Whereas the existence of such implicatures is rather uncontroversial
for plain occurrences of \emph{some}, it is still an issue of debate
whether comparable enrichments are also found in so-called
``embedded'' cases, where the scalar item \emph{some} occurs in the
scope of other logical operators. This paper deals with two such
cases.  In \as-sentences (mnemonic for \textit{all \dots some \dots})
as in (\ref{bsp:AE}) the scalar item \emph{some} is embedded the under
universal quantifier \emph{all}. In \es-sentences (mnemonic for
\textit{exactly one \dots some \dots}) like (\ref{bsp:GE}) \emph{some}
takes scope under the non-monotonic quantifier \emph{exactly one}.
According to current pragmatic theory, there are at least three
relevant candidate readings for \as- and \es-sentences: (i) a
\emph{literal reading} like in (\ref{bsp:AE-Literal}) and
(\ref{bsp:GE-Literal}) where \emph{some} has only its literal meaning;
(ii) a \emph{global reading} like in (\ref{bsp:AE-Global}) and
(\ref{bsp:GE-Global}) where the meaning of (\ref{bsp:AE}) and
(\ref{bsp:GE}) is enriched with the negation of the corresponding
sentences (\ref{bsp:AE-Alternative}) and (\ref{bsp:GE-Alternative})
respectively; and also (iii) a \emph{local reading} like in
(\ref{bsp:AE-Local}) and (\ref{bsp:GE-Local}) where \emph{some} is
interpreted as \emph{some but not all} in the scope of the embedding
quantifier.

@@

Given this plurality of hypothesized readings, the question arises:
how salient or preferred are these theoretically conceivable readings
compared to each other (if they are detectable by empirical means at
all)?  Addressing this question empirically is relevant because it
lies at the heart of a current debate about the nature of quantity
inferences and the demarkation between semantics and pragmatics. The
controversy is usually seen as one between two main competing
theoretical positions. \emph{Traditionalism} holds, in particular,
that local readings should not occur frequently unless marked by
special intonation. \emph{Grammaticalism} holds that local readings
are unproblematically available and, at least under the most prominent
of selection principles for candidate readings, even at least as
salient as the literal reading (see
Section~\ref{sec:grammaticalism}). To distinguish between these
opposing positions, it is therefore necessary to assess the relative
salience of readings for \as- and \es-sentences under conditions that
control for prosodic markedness.

A number of empirical studies have already examined sentences like
(\ref{bsp:AE}) and (\ref{bsp:GE})
\citep[e.g.][]{GeurtsPouscoulous2009:Embedded-Implic,CliftonDube2010:Embedded-Implic,ChemlaSpector2010:Experimental-Ev,BenzGotzner2014:Embedded-implic}. Unfortunately,
results from these studies do not provide uncontroversial
evidence. This is due to several reasons. Firstly, previous studies
have only accumulated limited evidence pertaining to the relative
salience of candidate readings of both types of sentences. Secondly,
as \citet{Tielvan-Tiel2012:Embedded-Scalar} and
\citet{GeurtsTielvan-Tiel2013:Embedded-Scalar} argue, the alleged
evidence for the availability of local readings of \as-sentences
suggested by studies of \citet{CliftonDube2010:Embedded-Implic} and
\citet{ChemlaSpector2010:Experimental-Ev}, might well be confounded
with what van Tiel and Geurts call \emph{typicality effects} (see
Section~\ref{sec:previous-studies} for discussion). Finally, and most
importantly, previous studies presented target sentences
visually. However, traditionalists acknowledge the availability of
local readings for prosodically marked utterances
\citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,ChemlaSpector2010:Experimental-Ev,Geurts2010:Quantity-Implic,Tielvan-Tiel2012:Embedded-Scalar,GeurtsTielvan-Tiel2013:Embedded-Scalar}. We
will address this extant position as the \emph{prosodic markedness
  hypothesis} and argue that, if intonation is hypothesized to play a
central role, it is vital to present target sentences auditorily, and
to control for effects of ``silent prosody'' that subjects may apply
when reading a sentence \citep[see][]{Bader98,Fodor98}.

This paper presents results form an experimental study designed to
deal with the above mentioned problems. We presented sentence
materials auditorily and explicitly manipulated intonational stress on
embedded scalar items. To cater for potential pictorial confounds,
such as from typicality, we employed an \emph{incremental verification
  task} in which parts of a to-be-evaluated picture were hidden and
only revealed piece-wise at the participants' request until they felt
able to give a binary truth-value judgement
\citep[see][]{Conroy2008}. This way we obtained categorical behavioral
data that is both more clearly indicative of the reading that subjects
assumed and more independent of any potential pictorial confounds, such
as the mentioned typicality effects. Moreover, this method also gives
information about reading preferences. We validated this by including
control conditions with ambiguous sentences with a well-known
preference on available readings.

The data obtained by this method is \emph{prima facie} problematic for
both traditionalism and grammaticalism. Contrary to the predictions of
traditionalism, we observed many answers indicative of local readings
of \es-sentences, irrespective of intonational markedness. But also
grammaticalism is incongruent with the observed pattern in our
data. Backed up by the \emph{strongest meaning hypothesis}
\citep{DalrympleKanazawa1998:Reciprocal-Expr} as a disambiguation
criterion \citep[as suggested by][]{ChierchiaFox2008:The-Grammatical},
grammaticalism predicts local readings to be the preferred readings,
but we found no evidence for that. More strongly even, the preference
order among putative readings suggested by our data cannot even in
principle be explained by comparisons of logical strength among
putative readings. In sum, our data shed doubt on both traditionalism
and grammaticalism in their currently most common forms. We conclude
the paper by some thoughts on how either position could be amended in
the light of our data.

The remainder of the paper is structured as
follows. Section~\ref{sec:get-know-your} elaborates on the three kinds
of relevant readings for our target
sentences. Section~\ref{sec:theories-predictions} works out the
predictions of traditionalism and grammaticalism about availability
and preference of readings for these
sentences. Section~\ref{sec:previous-studies} reviews related
experimental studies to the extent necessary to motivate our own
approach. Section~\ref{sec:exp} eventually contributes our
experimental design, analyses and results.

@@

There are two main theoretical positions which make different
predictions about the readings of \as- and \es-sentences
\citep[see][for
overview]{Horn2006:The-Border-Wars,Geurts2010:Quantity-Implic,Sauerland2012:The-Computation}. We
will refer to these as \mymark{traditionalism} and
\mymark{grammaticalism} and treat each one in turn. Since there is
some leeway in assessing the predictions for each approach (depending
on which of several additional assumptions to adopt), we will
distinguish different varieties of both of them. Predictions of all
relevant variants are summarized in Table~\ref{tab:predictions} on
page~\pageref{tab:predictions}.

@@

Traditionalism gets its name from its conservative stance towards
Grice's original theory of conversational implicatures
\citep{Grice1975:Logic-and-Conve}. Many author's have defended
traditionalist positions in this sense. Of the more recent literature,
we would consider as traditionalist, among others, contributions by
\citet{Spector2006:Scalar-Implicat},
\citet{Sauerland2004:Scalar-Implicat},
\citet{Russell2006:Against-Grammat},
\citet{vanRooijSchulz:ExhaustiveInterpretation},
\citet{Geurts2010:Quantity-Implic} or
\citet{Franke2011:Quantity-Implic}.

@@

As for \as- and \es-sentences, the Gricean recipe derives global
readings in a straightforward way. Consequently, traditionalism
predicts that both literal and global readings are available: literal
readings, because these form the starting point of pragmatic
reasoning; global readings because these may be arrived at by the
Gricean recipe.

Traditionalism's predictions about preferences between literal and
global readings depend on whether certain auxiliary assumptions
necessary to derive global readings by the Gricean recipe are
plausibly met. These auxiliary assumptions include relevance of the
extra information provided by the global reading, mutual awareness
that the stronger alternative has been a speaker option, the speaker's
competence about the issue, etc. Normally, traditionalist accounts
would assume that these extra assumptions are met. In that case,
traditionalism would predict that global readings should be preferred
over literal readings. On the other hand, if auxiliary assumptions are
implausible, traditionalism would predict that literal readings would
be preferred over global ones. Consequently, there are at least two
varieties of traditionalism that, depending on which additional
assumptions we would make, yield slightly different predictions:
\mymark{the strong variety of traditionalism} maintains that the
auxiliary assumptions of the Gricean recipe hold (e.g., as a matter of
strong default) and therefore predicts that global readings are
preferred over literal ones; \mymark{the weak variety of
  traditionalism} holds that the auxiliary assumptions are more
fragile and predicts that literal readings are preferred over global
ones.\fn{We mention for clarity that although weak traditionalism does
  not predict global readings to be preferred, it might still predict
  an \emph{epistemically weak implicature}, similar to the global
  reading, that the speaker is uncertain whether the stronger
  alternative is true. (See also the discussion in
  Section~\ref{sec:discussion-1})}

@@

On the other hand, as for \as-sentences, there is a traditionalist way
of deriving the local reading, namely by assuming that not only
(\ref{bsp:AE-Alternative}) is an alternative to (\ref{bsp:AE}), but
also the sentence in (\ref{bsp:AE-Alternatives-Extended}).

@@

\begin{exer}{bsp:AE-Alternative}
  \ex \mymark{All} of the students solved \mymark{all} of the problems.
\end{exer}

@@

\noindent Clearly, if we conjoin a literal reading of (\ref{bsp:AE})
with the negation of (\ref{bsp:AE-Alternatives-Extended}) we obtain
exactly the local reading. (Notice that the negation of
(\ref{bsp:AE-Alternatives-Extended}) entails the negation of
(\ref{bsp:AE-Alternative}), so it makes no difference (not) to add it
in this case.) Consequently, traditionalism does predict that the
local reading of \as-sentences is available if
(\ref{bsp:AE-Alternatives-Extended}) is an available alternative. We
therefore introduce another distinction: \mymark{restricted
  traditionalism} assumes that (\ref{bsp:AE-Alternatives-Extended}) is
not available and therefore predicts that the local reading for
\as-sentences is not available; in contrast, \mymark{unrestricted
  traditionalism} assumes that (\ref{bsp:AE-Alternatives-Extended}) is
available and so is the local reading.

@@

The grammatical approach, as described so far, is not yet a fully
articulated theory. To make concrete predictions, it must be
supplemented by a selection principle that determines which of the
many readings made available by the grammar actually obtain or are
preferred. Proponents of grammaticalism are aware of this and have
suggested some tentative disambiguation
strategies. \citet{Magri2011:Another-Argumen}, for example, opts for
obligatory presence of $\exh$ with variability in the set of relevant
alternatives. Another proposal is that readings are the more preferred
the better they answer the contextually given question under
discussion
\citep[e.g.][]{Fox2007:Free-Choice-and,GualminiHulsey2008:The-Question-An}. Yet
another proposal is to select readings by comparison of logical
strengths, as suggested by the \mymark{strongest meaning hypothesis}
of \citet{DalrympleKanazawa1998:Reciprocal-Expr}
\citep[see][]{FoxSpector:Economy-and-Emb,ChierchiaFox2008:The-Grammatical,Chierchia2012:FC-Nominals-and,Spector2014:Global-Positive}. We
will focus entirely on this latter selection principle, because it
seems to be the most prominent in the literature and because it makes
the clearest predictions.

@@

Taking stock, traditionalism and grammaticalism predict different
patterns of availability and preference for \as- and
\es-sentences. Most notably, traditionalism does not predict local
readings for \es-sentences to be available. Grammaticalism predicts
that all readings are available, but, given the strongest meaning
hypothesis, also comes with a clear indication of preference: literal
meanings are dispreferred. All predictions are summarized in
Table~\ref{tab:predictions}.

@@

Although traditionalism does not of itself predict local readings to
be available, many authors who adhere to a traditionalist position
propose that local readings are available if the embedded scalar item
is prosodically marked by contrastive stress
\citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,Geurts2010:Quantity-Implic,GeurtsTielvan-Tiel2013:Embedded-Scalar}. This
is taken to be continuous with other cases where pragmatic enrichments
can take scope under logical operators if the relevant focal accent is
present (\ref{bsp:Stress}).

@@

To date, empirical evidence for this assumption is still scarce. One
notable exception comes from a pilot study reported in
\citet{Frazier08}, in which participants were instructed to read
embedded and non-embedded versions of English \as-sentences. In the
embedded sentences (e.g. {\it All of the students wrote some of the
  official memos}), {\it some} was either capitalized or
non-capitalized. Prior to the experiment, participants were informed
that capitalizing corresponded to contrastive stress. The task
consisted in a forced-choice questionnaire with two given alternatives
(such as {\it All of the students wrote some but not all of the
  official memos} vs. {\it All of the students wrote at least some of
  the official memos}). Interestingly, strengthened interpretations
occurred rather often across all sentences in this task (59 \%), but
were not affected by capitalizing.\fn{Note that, unfortunately, the
  paper does not provide percentages for the embedded conditions
  alone, but only the means across sentence types.}
\citeauthor{Frazier08} concludes that accentuation did not affect the
silent reading data, but raises the possibility that prosodic effects
may have been present at least in a subset of the items (see
footnote~1 in \citet{Frazier08}, p.~330).

Another study relevant for the present considerations comes from
\citet{SchwarzClifton2008:Strengthening-o}, examining the effects of
contrastive accentuation of \emph{or} in non-embedded sentences like
{\it Mary will invite Fred or/OR Sam to barbecue}. After listening to
these sentences, participants were presented two alternative readings
({\it 1. She will invite Fred or Sam or possibly both}, or {\it 2.
  She will invite Fred or Sam but not both}).  The authors found a
significant impact of overtly realized contrastive accents on
implicature inferences: Besides a general advantage for
non-strengthened readings, focal accents significantly increased the
strengthened interpretation (from 16.4 \% to 28.6 \%). These results
are compatible with the "focus strengthening hypothesis" proposed by
the authors.

@@

  \subfloat[][Example of the \as-weak condition of
  \citet{ChemlaSpector2010:Experimental-Ev}]{
      \label{fig:Chemla-Spector}
  \begin{minipage}{0.45\linewidth}
    \begin{center}
      \includegraphics[scale=0.25]{../../pictures/paper/Chemla_Spector_2010_Critical_AE.png}\\
      \includegraphics[scale=0.25]{../../pictures/paper/Chemla_Spector_2010_RatingBar.png}
    \end{center}

  \end{minipage}
    }
   \begin{minipage}{6cm}
     \subfloat[][Results \as-condition]{
    \label{fig:CS-Results-as}
        \includegraphics[width=5.5cm]{../../pictures/paper/Chemla_Spector_2010_Results_AE.png}
  }

  \subfloat[test][Results \es-condition]{
    \label{fig:CS-Results-es}
    \includegraphics[width=5.5cm]{../../pictures/paper/Chemla_Spector_2010_Results_GE.png}
  }  
   \end{minipage}
        \caption{Example trial and results of
          \citeauthor{ChemlaSpector2010:Experimental-Ev}'s
          (\citeyear{ChemlaSpector2010:Experimental-Ev}) study.}
\end{figure}

@@

  \end{axis}
\end{tikzpicture}
		% \fbox{\includegraphics[width=5.5cm]{../../pictures/paper/duration_ge.png}}
	    \label{fig:duration_ge}
	}
	\caption[]{Durational values (in ms) for 
	the single regions for \as-sentences (a) and \es-sentences (b).}
	\label{fig:duration_targets}
\end{figure}

>>>>

\usepackage{gb4e_micha}

\usepackage{mycommands}

@@

\title{Embedded Scalars, Preferred Readings \& Prosody: {A}n
  Experimental Revisit} 
\author{% Fabian
  % Schlotterbeck, Michael Franke and Petra Augurzky
} 
\date{}

@@

Whereas the existence of such implicatures is rather uncontroversial
for plain occurrences of \emph{some}, it is still an issue of debate
whether comparable enrichments are also found in so-called
``embedded'' cases, where the scalar item \emph{some} occurs in the
scope of other logical operators. This paper deals with two such
cases.  In \as-sentences (mnemonic for \textit{all \dots some \dots})
as in (\ref{bsp:AE}) the scalar item \emph{some} is embedded the under
universal quantifier \emph{all}. In \es-sentences (mnemonic for
\textit{exactly one \dots some \dots}) like (\ref{bsp:GE}) \emph{some}
takes scope under the non-monotonic quantifier \emph{exactly one}.
Current theories, have proposed at least three candidate readings
for \as- and \es-sentences: (i) a \emph{literal reading} like in (\ref{bsp:AE-Literal}) and
(\ref{bsp:GE-Literal}) where \emph{some} has only its literal meaning;
(ii) a \emph{global reading} like in (\ref{bsp:AE-Global}) and
(\ref{bsp:GE-Global}) where the meaning of (\ref{bsp:AE}) and
(\ref{bsp:GE}) is enriched with the negation of the corresponding
sentences (\ref{bsp:AE-Alternative}) and (\ref{bsp:GE-Alternative})
respectively; and also (iii) a \emph{local reading} like in
(\ref{bsp:AE-Local}) and (\ref{bsp:GE-Local}) where \emph{some} is
interpreted as \emph{some but not all} in the scope of the embedding
quantifier.

@@

Given this plurality of hypothesized readings, the question arises:
how salient are these theoretically conceivable readings
compared to each other (if they are detectable by empirical means at
all)?  Addressing this question empirically is relevant because it
lies at the heart of a current debate about the nature of quantity
inferences and the demarkation between grammar (i.e. syntax/semantics)
and domain-general reasoning procedures (i.e. pragmatics). The controversy
is usually seen as one between two main competing theoretical positions
\citep[see][for a detailed comparison of the two]{ChemlaSingh2014:Remarks-on-the-}.
Simplifying things for now, these two types of theories make clearly different
predictions about how salient the local readings, in particular, should be.
The first position which we refer to as \mymark{traditionalism} (Chemla \& Singh’s ``Gricean approach'') holds that local readings should not be salient at all.
The second one which we call \mymark{grammaticalism}
(Chemla \& Singh’s ``grammatical approach'') holds that local readings
are unproblematically available and even at least as salient
as the literal ones (see Section \ref{sec:theories-predictions} for a more
thorough exposition of the theories and their predictions).

That matters actually are not as simple as just described is reflected
by lively discussions about which conclusions are permitted by previous
experimental research \citep[e.g.][]{GeurtsPouscoulous2009:Embedded-Implic,CliftonDube2010:Embedded-Implic,ChemlaSpector2010:Experimental-Ev,BenzGotzner2014:Embedded-implic}. The results of these studies
were discussed controversially because of several specific reasons. Firstly,
and most importantly, previous studies presented target sentences visually.
However, traditionalists often acknowledge the availability of local readings for
prosodically marked utterances, albeit not as the result of
a standard scalar implicature but of a different pragmatic process triggered by
prosodic markedness \citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,ChemlaSpector2010:Experimental-Ev,Geurts2010:Quantity-Implic,Tielvan-Tiel2012:Embedded-Scalar,GeurtsTielvan-Tiel2013:Embedded-Scalar}. Under this view, evidence for the availability of local readings \citep[see][]{CliftonDube2010:Embedded-Implic,ChemlaSpector2010:Experimental-Ev} may be
an effect of “silent prosody”  \citep[see e.g.][]{Bader98,Fodor98}. Secondly, as \citet{Tielvan-Tiel2012:Embedded-Scalar} and \citet{GeurtsTielvan-Tiel2013:Embedded-Scalar} argue,
the alleged evidence for the availability of local readings of \as-sentences, might well be
confounded with “typicality effects”  (see Section~\ref{sec:previous-studies} for discussion).
Finally, previous studies have only accumulated limited evidence pertaining to the relative
salience of candidate readings of sentences like (\ref{bsp:AE}) and (\ref{bsp:GE}) (see
Section~\ref{sec:previous-studies} for discussion).

More generally, two prerequisites have to be met in order to make use of
experimental data to decide between theoretical positions regarding the
computation of quantity inferences. Firstly, both traditionalism and grammaticalism
have to be amended with additional assumptions to derive testable
predictions about the relative salience of candidate readings. For example,
hypothezised effects of prosodic marking have to be taken into account before
we can test traditionalism empirically using sentences  (\ref{bsp:AE}) and (\ref{bsp:GE}).
We will address this extant position as the \mymark{prosodic markedness hypothesis}
and argue that, if prosody is hypothesized to play a central role, it is vital
to present target sentences auditorily or to control for effects of  “silent prosody”
that subjects may apply when reading a sentence. Secondly, the relative
salience of candidate readings has to be operationalized properly, i.e. we
have to devise methods to measure relative salience. For example, typicality
effects and logical dependencies between readings have to be controlled for
when evaluating speaker judgments in terms of the salience of candidate readings.
Both of these prerequisites are related to formulating what \citet{ChemlaSingh2014:Remarks-on-the-}
call ``linking functions'' which connect the core theories to the dependent
variables of an experiment. Without proper linking functions it is hard
(or impossible) to test traditionalism or grammaticalism empirically.

This paper presents results form an experimental study designed to deal with
the mentioned problems. The focus is on testing certain formulations of traditionalism
and grammaticalsim that are explicit enough to derive testable predictions about the
relative salience of candidate readings. For practical reasons, we choose what we consider
the most prominent of such formulations. In order to address the prosodic markedness
hypothesis, we presented sentence materials auditorily and explicitly manipulated contrastive
stress on embedded scalar items. In order operationalize the relative salience of candidate
readings, we employed an \mymark{incremental verification task} in which parts of a to-be-evaluated
picture were hidden and only revealed piece-wise at the participants’ request until they felt able
to give a binary truth-value judgement \citep[see][]{Conroy2008}. This way, we catered for
potential pictorial confounds, such as from typicality. To analyze the obtained data in terms
of relative salience of candidate readings, we furthermore employed a statistical model of
how the salience of readings guided participants judgments in the incremental verification task. We
validated this method by including control conditions testing ambiguous sentences with a
well-known preference on available readings. We argue that this method provides
categorical behavioral data that is both clearly indicative of the reading preferences
among participants and independent of any potential pictorial confounds, such as
the mentioned typicality effects.

The data obtained by this method is \emph{prima facie} problematic for both
traditionalism and grammaticalism (or at least what we consider the most
prominent versions thereof). However, we want to stress from the outset
that, while the experimental results allow us to derive restrictions on which
linking functions are conceivable for traditionalism and grammaticalism, conclusions
about the general validity of the two core theories will be limited
\citep[cf.][]{ChemlaSingh2014:Remarks-on-the-} because these hardly make falsifiable
predictions without the necessary linking functions. Contrary to the predictions
of common versions of traditionalism, we observed many answers indicative of
local readings of \es-sentences, irrespective of prosodic markedness. But also
prominent versions of grammaticalism are incongruent with the observed data.
Backed up by the \mymark{strongest meaning hypothesis}
\citep{DalrympleKanazawa1998:Reciprocal-Expr} as a
disambiguation criterion \citep[as suggested by][]{ChierchiaFox2008:The-Grammatical},
grammaticalism predicts local readings to be the preferred ones, but
we found no evidence for that. More strongly even, the preference order among
putative readings suggested by our data cannot even in principle be
explained by comparisons of logical strength among putative
readings. In sum, our data shed doubt on both traditionalism and grammaticalism
in their currently most common forms. We conclude the paper by some thoughts on
how either position could be amended in the light of our data.

The remainder of the paper is structured as
follows. Section~\ref{sec:get-know-your} elaborates on the three kinds
of relevant readings for our target
sentences. Section~\ref{sec:theories-predictions} works out the
predictions of traditionalism and grammaticalism (plus prominent linking functions) 
about availability and relative salience of readings for these
sentences. Section~\ref{sec:previous-studies} reviews related
experimental studies to the extent necessary to motivate our own
approach. Section~\ref{sec:exp} eventually contributes our
experimental design, analyses and results.

@@

There are two main theoretical positions which make different 
predictions about the readings of \as- and \es-sentences \citep[see][for
overview]{Horn2006:The-Border-Wars,Geurts2010:Quantity-Implic,Sauerland2012:The-Computation,ChemlaSingh2014:Remarks-on-the-}. We will refer to these as \mymark{traditionalism} and \mymark{grammaticalism}
and treat each one in turn.  As already mentioned in the introduction there is some
leeway in assessing the predictions for each approach depending on which of several
additional assumptions to adopt. Therefore, we will distinguish different varieties
of both of them. While these are certainly not the only possible varieties, they are,
in our perception, the most prominent ones. Focusing on exactly these thus has
practical relevance. Their predictions are summarized in Table~\ref{tab:predictions}
on page~\pageref{tab:predictions}. Below, in the discussion section
(section~\ref{sec:discussion-1}), further conceivable varieties of traditionalism
and grammaticalism will be discussed.

@@

Traditionalism gets its name from its conservative stance towards
Grice's original theory of conversational implicatures
\citep{Grice1975:Logic-and-Conve}. Many authors have defended
traditionalist positions in this sense. Of the more recent literature,
we would consider as traditionalist, among others, contributions by
\citet{Spector2006:Scalar-Implicat},
\citet{Sauerland2004:Scalar-Implicat},
\citet{Russell2006:Against-Grammat},
\citet{vanRooijSchulz:ExhaustiveInterpretation},
\citet{Geurts2010:Quantity-Implic} or
\citet{Franke2011:Quantity-Implic}.

@@

As for \as- and \es-sentences, the Gricean recipe derives global
readings in a straightforward way. Consequently, traditionalism
predicts that both literal and global readings are available:  literal
readings, because these are the result of semantic interpretation
and form the starting point of pragmatic reasoning; global readings
because these may be arrived at by the Gricean recipe.

Traditionalism's predictions about relative salience of literal and
global readings depend on whether certain auxiliary assumptions
necessary to derive global readings by the Gricean recipe are
plausibly met. These auxiliary assumptions include relevance of the
extra information provided by the global reading, mutual awareness
that the stronger alternative has been a speaker option, the speaker's
competence about the issue, etc. Normally, traditionalist accounts
would assume that these extra assumptions are met. In that case,
traditionalism would predict that global readings should be preferred
over literal readings. On the other hand, if these extra assumptions
are implausible, traditionalism would predict that literal readings
are preferred over global ones \citep[see][for experimental evidence
indicating that manipulation of speaker knowledgeability indeed
affects the rate of quantity implicatures drawn by the listener
for unembedded occurrences of \emph{some}]{GoodmanStuhlmuller2013:Knowledge-and-I}.

Consequently, there are at least two varieties of traditionalism that,
depending on which extra assumptions we make, yield slightly
different predictions: the \mymark{the strong variety of traditionalism}
maintains that the extra assumptions of the Gricean recipe hold
(e.g., as a matter of strong default) and therefore predicts that global
readings are preferred over literal ones; \mymark{the weak variety of
traditionalism} holds that the auxiliary assumptions are more fragile
and context dependent and thus predicts that literal readings may
often be preferred over global ones. In Table~\ref{tab:predictions}
(p.~\pageref{tab:predictions}), this prediction of weak traditionalism
is captured by a preference of literal over global readings because it
may \emph{a priori} seem implausible from the perspective of weak
traditionalism that all the necessary assumptions to derive global
readings are met. \fn{We mention for clarity that although weak traditionalism does
  not predict global readings to be generally preferred, it might still predict
  an \emph{epistemically weak implicature}, similar to the global
  reading, that the speaker is uncertain whether the stronger
  alternative is true. (See also the discussion in
  Section~\ref{sec:discussion-1})} For weak traditionalism, it is of course an empirical
task to determine under which circumstances the auxiliary assumptions
are met.

@@

On the other hand, as for \as-sentences, there is a traditionalist way
of deriving the local reading, namely by assuming that not only
(\ref{bsp:AE-Alternative}) is an alternative to (\ref{bsp:AE}), but
also the sentence in (\ref{bsp:AE-Alternatives-Extended}) \citep[e.g.][]{Sauerland2004:Scalar-Implicat}.

@@

\begin{exer}{bsp:AE-Alternative}
  \ex \label{bsp:AE-Alternatives-Standard}\mymark{All} of the students solved \mymark{all} of the problems.
\end{exer}

@@

\noindent Clearly, if we conjoin a literal reading of (\ref{bsp:AE})
with the negation of (\ref{bsp:AE-Alternatives-Extended}) we obtain
exactly the local reading. (Notice that the negation of
(\ref{bsp:AE-Alternatives-Extended}) entails the negation of
(\ref{bsp:AE-Alternative}), so it makes no difference (not) to add it
in this case.) Consequently, traditionalism does predict that the
local reading of \as-sentences is available if
(\ref{bsp:AE-Alternatives-Extended}) is an available alternative. We
therefore introduce another distinction: \mymark{restricted
  traditionalism} assumes that (\ref{bsp:AE-Alternatives-Extended}) is
not available and therefore predicts that the local reading for
\as-sentences is not available; in contrast, \mymark{unrestricted
  traditionalism} assumes that
(\ref{bsp:AE-Alternatives-Extended}) is available and so is the
local reading.\fn{The term traditionalism may be misleading here
because traditionalists usually assume that scalar implicatures should
only be computed when a sentence is uttered in a context in which a
logically stronger alternative is relevant \cite{ChemlaSingh2014:Remarks-on-the-}. However, the alternative
in (\ref{bsp:AE-Alternatives-Extended}) is not stronger than
(\ref{bsp:AE}). For completeness sake, we still decided to subsume
“unrestricted traditionalism” under traditionalism because, once
alternatives like (\ref{bsp:AE-Alternatives-Extended}) are acknowledged,
the local reading of \as-sentences can be derived in a
straightforward traditionalist manner \citep[see also][]{ChemlaSpector2010:Experimental-Ev}
who call this type of theory ``unrestricted globalism'').}

@@

The grammatical approach, as described so far, does not
make testable predictions about the relative salience of our three
candidate readings. In order to derive predictions about reading preferences,
a selection principle is needed that determines which of the
many readings made available by the grammar actually obtain or are
preferred. Proponents of grammaticalism are aware of this and have
suggested some tentative disambiguation
strategies. \citet{Magri2011:Another-Argumen}, for example, opts for
obligatory presence of $\exh$ with variability in the set of relevant
alternatives.  In the approach of \citet{Magri2011:Another-Argumen},
alternatives may be pruned entirely in the extreme case. In that case, all occurrences
of $\exh$ become vacuous resulting in a literal reading. However,
\citet{Magri2011:Another-Argumen} does not formulate an explicit theory
about which alternatives enter into the computation of sentence meaning
under what circumstances. Therefore, it is not clear what his approach
predicts about the relative salience of the candidate readings.

Other proponents of grammaticalism assume that insertion of $\exh$ is optional.
These approaches treat the ambiguity between our candidate readings as a
structural one which resembles syntactic ambiguities. In order to derive
predictions about reading preferences a mechanism of ambiguity resolution
is needed in these approaches. One proposal is that readings are the
more preferred the better they answer the contextually given question
under discussion \citep[e.g.][]{Fox2007:Free-Choice-and,GualminiHulsey2008:The-Question-An}.
Another proposal is to select readings by comparison of logical strengths, as suggested by the \mymark{strongest meaning hypothesis}
of \citet{DalrympleKanazawa1998:Reciprocal-Expr}
\citep[see][]{FoxSpector:Economy-and-Emb,ChierchiaFox2008:The-Grammatical,Chierchia2012:FC-Nominals-and,Spector2014:Global-Positive}. For now, we focus
exclusively on this latter selection principle, because it seems to be
the most prominent in the literature and because it makes the clearest
predictions. In the discussion section (section~\ref{sec:discussion-1})
alternative selection principles will be reconsidered.

@@

Taking stock, traditionalism and grammaticalism make different
predictions about the relative salience (and thus preference) of our candidate
readings. Most notably, traditionalism does not predict local
readings for \es-sentences to be available at all while grammaticalism does.
Grammaticalism predicts that all candidate readings are available and,
employing the strongest meaning hypothesis as selection principle, also
comes with a clear prediction about preference: literal meanings are dispreferred.
All predictions are summarized in Table~\ref{tab:predictions}.

@@

Although restricted traditionalism does not of itself predict local readings to be
available at all and even unrestricted traditionalism does not predict local
readings for \es-sentences,  many authors who adhere to a traditionalist position
propose that local readings are available if the embedded scalar item
is prosodically marked by contrastive stress \citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,Geurts2010:Quantity-Implic,GeurtsTielvan-Tiel2013:Embedded-Scalar}. This
is taken to be continuous with other cases where pragmatic enrichments can
take scope under logical operators if the relevant focal accent is present (\ref{bsp:Stress}).

@@

To date, empirical investigations of this assumption are still scarce.  One
notable exception is a pilot study reported in
\citet{Frazier08}, in which participants were instructed to read
embedded and non-embedded versions of English \as-sentences. In the
embedded sentences (e.g. {\it All of the students wrote some of the
  official memos}), {\it some} was either capitalized or
non-capitalized. Prior to the experiment, participants were informed
that capitalizing corresponded to contrastive stress. The task
consisted in a forced-choice questionnaire with two given alternative
paraphrases  (such as {\it All of the students wrote some but not all of the
  official memos} vs. {\it All of the students wrote at least some of
  the official memos}). Interestingly, strengthened interpretations
occurred rather often across all sentences in this task (59 \%), but
were not affected by capitalizing.\fn{Note that, unfortunately, the
  paper does not provide percentages for the embedded conditions
  alone, but only the means across sentence types.}
\citeauthor{Frazier08} concludes that accentuation did not affect the
silent reading data, but raises the possibility that prosodic effects
may have been present at least in a subset of the items (see
footnote~1 in \citet{Frazier08}, p.~330).

Another study relevant for the present considerations comes from
\citet{SchwarzClifton2008:Strengthening-o}, examining the effects of
contrastive accentuation of \emph{or} in non-embedded sentences like
{\it Mary will invite Fred or/OR Sam to barbecue}. After listening to
these sentences, two alternative paraphrases were presented to
the participants (e.g. {\it She will invite Fred or Sam or possibly both} vs. {\it
  She will invite Fred or Sam but not both}).  The authors found a
significant impact of overtly realized contrastive accents on
implicature inferences: Besides a general advantage for
non-strengthened readings, focal accents significantly increased the
strengthened interpretation (from 16.4 \% to 28.6 \%). These results
are compatible with the "focus strengthening hypothesis" proposed by
the authors.

@@

  \subfloat[][Example of the \as-weak condition of
  \citet{ChemlaSpector2010:Experimental-Ev}]{
      \label{fig:Chemla-Spector}
  \begin{minipage}{0.45\linewidth}
    \begin{center}
      \includegraphics[scale=0.25]{pictures/paper/Chemla_Spector_2010_Critical_AE.png}\\
      \includegraphics[scale=0.25]{pictures/paper/Chemla_Spector_2010_RatingBar.png}
    \end{center}

  \end{minipage}
    }
   \begin{minipage}{6cm}
     \subfloat[][Results \as-condition]{
    \label{fig:CS-Results-as}
        \includegraphics[width=5.5cm]{pictures/paper/Chemla_Spector_2010_Results_AE.png}
  }

  \subfloat[test][Results \es-condition]{
    \label{fig:CS-Results-es}
    \includegraphics[width=5.5cm]{pictures/paper/Chemla_Spector_2010_Results_GE.png}
  }  
   \end{minipage}
        \caption{Example trial and results of
          \citeauthor{ChemlaSpector2010:Experimental-Ev}'s
          (\citeyear{ChemlaSpector2010:Experimental-Ev}) study.}
\end{figure}

@@

  \end{axis}
\end{tikzpicture}
		% \fbox{\includegraphics[width=5.5cm]{pictures/paper/duration_ge.png}}
	    \label{fig:duration_ge}
	}
	\caption[]{Durational values (in ms) for 
	the single regions for \as-sentences (a) and \es-sentences (b).}
	\label{fig:duration_targets}
\end{figure}
